\documentclass[11pt]{report}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\alph{subsection}}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{titlesec}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\begin{document}

\begingroup  
    \centering
    \Large Optimal estimation of intraday `true value' using the Glosten-Milgrom model\\
    \large Isaac Drachman\par
\endgroup
   
\section*{}
    We wish to statistically model the `true value' of a traded asset over a
    time period solely by utilizing its order flow. The primary
    object of study is therefore $\mu_t$, the true value after the $t$-th trade. We say that
    $\mu_t$ follows a distribution $F_t$. We let our best estimate
    be $\hat{\mu}_t = \mathbb{E}F_t$.\\\\    
    We consider the data $(m_0,\,X)$, where $m_0$ is the initial midpoint price and $X$ is a 
    sequence of 
    trades $x_1,\,x_2,\,...,\,x_T$. The $t$-th trade $x_t$ is the pair $(d_t,\,p_t)$, where $d_t = +1$
    or $-1$ for a market buy or a market sell, respectively, and $p_t$ is price at 
    which the trade occurred. We specify the first prior distribution $F_0$ as Normal
    with mean $m_0$ and std. deviation $\sigma$, which will be a parameter of our model. Our
    first best estimate is $\hat{\mu}_0 = m_0$.\\\\
    From the Glosten-Milgrom microstructure model, we say that all traders are either 
    perfectly informed (who know $\mu_t$) or uninformed (noisy trading) with the 
    following specifications (where $b_t,\,a_t$ are bid/ask after trade $t$)
    \begin{align*}
    P(\text{trade made by informed trader}) & = \alpha \\
    P(\mu_t > a_t\,|\,\text{informed bought}) & = 1 \\
    P(\mu_t < b_t\,|\,\text{informed sold}) & = 1 \\
    P(\text{uninformed buys when trades}) & = \eta \\
    \end{align*} 
    After witnessing trade $x_t$ we update $F_t$ to a posterior distribution $F_{t+1}$ 
    using this$\text{}^{[1]}$. We explicitly
    modify the probability distribution function for a trade with $d_t = +1$ (i.e. market buy)
    \[
    f_{t+1}(p) = f_t(p) \times
    \bigg\{\begin{array}{cc}
        (1 - \alpha)\eta + \alpha & p > a_t \\
        1 - \alpha - (1 - \alpha)\eta & p \leq a_t \\
    \end{array} 
    \]    
    After witnessing a trade with $d_t = -1$ (i.e. market sell)
    \[
    f_{t+1}(p) = f_t(p) \times
    \bigg\{\begin{array}{cc}
        (1 - \alpha)\eta + \alpha & p < b_t \\
        1 - \alpha - (1 - \alpha)\eta & p \geq b_t \\
    \end{array} 
    \]    
    We set $a_t,\,b_t = p_t$, i.e. we have that the price at which the trade occurred 
    was on the bid/ask. These probability distributions then need to be normalized.\\\\
    When coding this model we create the sequence of vectors 
    $\{\mathbf{p}^t\}_{t \in \{0,\,1,\,...,\,T\}}$ such that each $\mathbf{p}^t$ has
    $\floor{800\sigma}$ components with
    \[
    p_i^t = P(\mu_t = m_0 - 4\sigma + i/100) = f_t(m_0 - 4\sigma + i/100)
    \]
    This allows a discretization of $\mu_t$ and its distribution $F_t$ into 
    the minimum increment (tick) of one cent. We denote the price $m_0 - 4\sigma + i/100$ 
    as $v_i$ for convenience. The expectation $\hat{\mu}_t$ can then be computed by
    \begin{align*}
    \hat{\mu}_t & = \mathbb{E}F_t = \int_{-\infty}^{\infty} p\,f_t(p) \,\,\mathrm{d}p \\
    & \approx \mathbf{v}\cdot\mathbf{p}^t
    = \sum_{i=0}^{\floor{800\sigma}} v_i\,f_t(v_i)
    \end{align*}

\end{document}